Predicting Bike Usage at UofT St. George with Bayesian Poisson Regression

### 2024-12-03 paper/paper.qmd
figures renamed
figures renamed

```{r, fig.pos="H"}
#| label: fig-PPvsFV
#| fig-cap: "Pearson Residuals vs Fitted Values: \"Galbraith Rd / King's College Rd\" Model"
#| echo: false
#| message: false
#| warning: false
options(scipen = 999)
poisson_glm <- readRDS(here::here("models/College_St___Huron_St.rds"))
data <- read_parquet(here::here("data/02-analysis_data/start.parquet")) %>% filter(station_name == "Galbraith Rd / King's College Rd
")%>%
    mutate(
      hour = hour(time),
      day = day(time),
      month = month(time),
      year = year(time)
    )

@@

```{r, fig.pos="H"}
#| label: fig-PPplot
#| fig-cap: "Posterior Predictive Checks: \"Galbraith Rd / King's College Rd\" Model"
#| echo: false
#| message: false
#| warning: false
# Posterior Predictive Checks
pp_check(poisson_glm, plotfun = "dens_overlay", nreps = 100) +
  labs(
    x = "Usage",  
    y = "Estimated density"         
  ) +
   yaxis_text()
```
The credible intervals shown in @tbl-crediinte highlight several strengths of the model of the "Galbraith Rd / King's College Rd" station. Key variables such as hour, month, and year have narrow credible intervals that do not include zero, indicating their significant and consistent influence on the response variable. This demonstrates the model’s ability to effectively capture important trends and relationships in the data, particularly those related to time and seasonal effects. Additionally, the relatively small width of these intervals reflects the stability and reliability of parameter estimates, suggesting that the model is well-calibrated and robust in its predictions. The intercept, while having a broader credible interval, provides a reasonable baseline estimate, reflecting the overall level of the response variable.

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-crediinte
#| tbl-cap: "Credible intervals of model coefficients: \"Galbraith Rd / King's College Rd\" Model"
posterior_draws <- as.matrix(poisson_glm)

>>>>

```{r, fig.pos="H"}
#| label: fig-PPvsFV
#| fig-cap: "Pearson Residuals vs Fitted Values for \"Galbraith Rd / King's College Rd\" Model"
#| echo: false
#| message: false
#| warning: false
options(scipen = 999)
poisson_glm <- readRDS(here::here("models/College_St___Huron_St.rds"))
data <- read_parquet(here::here("data/02-analysis_data/start.parquet")) %>% filter(station_name == "Galbraith Rd / King's College Rd
")%>%
    mutate(
      hour = hour(time),
      day = day(time),
      month = month(time),
      year = year(time)
    )

@@

```{r, fig.pos="H"}
#| label: fig-PPplot
#| fig-cap: "Posterior Predictive Checks for \"Galbraith Rd / King's College Rd\" Model"
#| echo: false
#| message: false
#| warning: false
# Posterior Predictive Checks
pp_check(poisson_glm, plotfun = "dens_overlay", nreps = 100) +
  labs(
    x = "Usage",  
    y = "Estimated density"         
  ) +
   yaxis_text()
```
The credible intervals shown in @tbl-crediinte highlight several strengths of the model of the "Galbraith Rd / King's College Rd" station. Key variables such as hour, month, and year have narrow credible intervals that do not include zero, indicating their significant and consistent influence on the response variable. This demonstrates the model’s ability to effectively capture important trends and relationships in the data, particularly those related to time and seasonal effects. Additionally, the relatively small width of these intervals reflects the stability and reliability of parameter estimates, suggesting that the model is well-calibrated and robust in its predictions. The intercept, while having a broader credible interval, provides a reasonable baseline estimate, reflecting the overall level of the response variable.

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-crediinte
#| tbl-cap: "Credible intervals of model coefficients for \"Galbraith Rd / King's College Rd\" Model"
posterior_draws <- as.matrix(poisson_glm)
